Adapting Duplicate Filters to a Sliding Window Context

### 2020-03-03 qhtv2.tex
Cleanup

\documentclass[sigconf]{acmart}

\usepackage{xspace}
\usepackage{centernot}
\usepackage{amsmath}

\newcommand{\FPR}{\textsf{FPR}\xspace}
\newcommand{\FNR}{\textsf{FNR}}
\newcommand{\DUPLICATE}{\textsf{DUPLICATE}\xspace}
\newcommand{\UNSEEN}{\textsf{UNSEEN}\xspace}
\newcommand{\todo}[1][]{{\color{red}{TODO: #1}}}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

%\copyrightyear{2018}
%\acmYear{2018}
%\setcopyright{acmlicensed}
%\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
%\acmPrice{15.00}
%\acmDOI{10.1145/1122445.1122456}
%\acmISBN{978-1-4503-9999-9/18/06}

%
% These commands are for a JOURNAL article.
%\setcopyright{acmcopyright}
%\acmJournal{TOG}
%\acmYear{2018}\acmVolume{37}\acmNumber{4}\acmArticle{111}\acmMonth{8}
%\acmDOI{10.1145/1122445.1122456}

%
% Submission ID. 
% Use this when submitting an article to a sponsored event. You'll receive a unique submission ID from the organizers
% of the event, and this ID should be used as the parameter to this command.
%\acmSubmissionID{123-A56-BU3}

%
% The majority of ACM publications use numbered citations and references. If you are preparing content for an event
% sponsored by ACM SIGGRAPH, you must use the "author year" style of citations and references. Uncommenting
% the next command will enable that style.
%\citestyle{acmauthoryear}

@@

%
% The "author" command and its associated commands are used to define the authors and their affiliations.
% Of note is the shared affiliation of the first two authors, and the "authornote" and "authornotemark" commands
% used to denote shared contribution to the research.
\author{R\'emi G\'eraud-Stewart}
\affiliation{%
  \institution{D\'epartement d'informatique de l'ENS, \'Ecole normale sup\'erieure, CNRS, PSL Research University}
  \city{Paris}
  \state{France}
}
\affiliation{%
	\institution{Ingenico Labs Advanced Research}
	\city{Paris}
	\state{France}
}
\email{remi.geraud@ens.fr}

\author{Marius Lombard-Platet}
\affiliation{%
  \institution{D\'epartement d'informatique de l'ENS, \'Ecole normale sup\'erieure, CNRS, PSL Research University}
  \city{Paris}
  \country{France}
}
\affiliation{%
\institution{Be-Studys}
\city{Geneva}
\country{Switzerland}
}
\email{marius.lombard-platet@ens.fr}

\author{David Naccache}
\affiliation{%
  \institution{D\'epartement d'informatique de l'ENS, \'Ecole normale sup\'erieure, CNRS, PSL Research University}
  \city{Paris}
  \country{France}
}
\affiliation{%
	\institution{Ingenico Labs Advanced Research}
	\city{Paris}
	\state{France}
}
\email{david.naccache@ens.fr}

%
% By default, the full list of authors will be used in the page headers. Often, this list is too long, and will overlap
% other information printed in the page headers. This command allows the author to define a more concise list
% of authors' names for this purpose.
%\renewcommand{\shortauthors}{G\'eraud-Stewart et al.}

>>>>

\input{preamble.tex}

@@

\author{Rémi Géraud-Stewart}
\affiliation{%
  \institution{Département d'informatique de l'ENS, école normale supérieure, CNRS, PSL Research University}
  \city{Paris}
  \state{France}
}
\email{remi.geraud@ens.fr}

\author{Marius Lombard-Platet}
\affiliation{%
  \institution{Département d'informatique de l'ENS, école normale supérieure, CNRS, PSL Research University}
  \city{Paris}
  \country{France}
}
\affiliation{%
\institution{Be-Studys}
\city{Geneva}
\country{Switzerland}
}
\email{marius.lombard-platet@ens.fr}

\author{David Naccache}
\affiliation{%
  \institution{Département d'informatique de l'ENS, école normale supérieure, CNRS, PSL Research University}
  \city{Paris}
  \country{France}
}
\email{david.naccache@ens.fr}
